Implications of Measurement Errors in Water Use Estimates for Water Management

### 2024-11-13 Writing/manuscript_typst.qmd
minor edits

We now look at simple two-farm examles to build intuition behind the profit loss due to the use of proxy quota in place of water quota. @fig-illust-homegeneous presents a case with two homegeneous farmers under water and proxy quota. The red dotted lines indicate the effective water quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is `r round(opt_w, digits = 2)` inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amout of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes `r pi_dif_2` less under the water quota system compared to the proxy quota system. However, Farmer A makes `r -pi_dif_1` more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respsect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to revmoing an inch of water from 10 inches.

```{r}
#| label: fig-illust-homegeneous
#| fig-cap: "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homegeneous producers"
#| warning: false
knitr::include_graphics("figures/g_illustration_homogeneous.png")
```

@@

@fig-trading-profit-illustration illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in @fig-illust-homegeneous. In this illustration, the same water quota of 7 is allocated for both farmers under the water-based systems. No water quota trading would happen as the marginal profit of water is already equated at water use of 7. Under the proxy-base quota system, proxy quota of 7 is allocated for both farmers, but the effective water quota for farmers A and B are 4 and 7, respectively. Once trading of proxy quota is alllowed, farmer A would buy `r farmer_A_purchase` proxy quota from farmer B. At these production levels, the marginal profit of quota (not water) are equated acros the farmers and no further transfer between them would happen. Trading of proxy quota improves the overall profit to `r profit_after_trade_proxy` $/acre from `r profit_before_trade_quota` $/acre.

@@

While water-quota and proxy-quota trading perform about the same, water-quota always leads to a higher total profit for a given level of realized water use. In other words, to achieve a certain water use goal, water-quota trading is always to more cost-effective than proxy-quota trading. Under water-quota trading, the margial profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use. Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the margial profit of water (See Appendix ... for a mathematical proof). However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in @fig-trading-profit. This point is well-illustrated in @fig-trading-profit-illustration, where total profit per acre is `r profit_after_trade_water` and `r profit_after_trade_proxy` under the water-quota and proxy-quota trading system, respsectively.

@fig-trading-profit presents the simualtion results of proxy-quota and water-quota trading systems added to @fig-profit-quota-water-het. As you can see at all levels of production heterogeneity levels and the degres of measurement errors, proxy-quota and water-quota trading systems perform almost identical at all levels of realized water use (water-quota trading is always slightly better than proxy-quota trading as explained earlier). Not surprisingly, the benefit of allowing for trading is greater when the degree of measurement errors is larger.

@@

@fig-distributional-equity presents the cumulative probability of the ratio of profit under the proxy-based relative to water-based system for quota (red) and permit trading (blue). Ratio of less than 1 indicates making less profit under the proxy-based system compared to the water-based system. If farmers make just as much profit under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1. For example, under the high degree of measurement error and medium heterogenenity scenario, some farmers would make about the half of what they would make under the water quota system. At the lower end of the distribution are farmers who would be constrained severely by water quota, but whose water use estiamtes are much higher than their actual water use. At the higher end of the distribution are farmers who would be constrained by water quota, but whose water use estiamtes are much lower than their actual water use. Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves. If they discover the over-estimation of their water use, they may appeal to legal actions against the administrator for their unfair treatment. Allowind quota trading greatly diminishes the distributional inequality, though not completely. This is because unfortunate farmers who suffered from over-estimation of their water use can now at least purchase proxy quota to increase their production level.

>>>>

We now look at simple two-farm examples to build intuition behind the profit loss due to the use of proxy quota in place of water quota. @fig-illust-homogeneous presents a case with two homogeneous farmers under water and proxy quota. The red dotted lines indicate the effective water quota. Under the water quota system, both farmers receive 7 inches of water quota. Since the unconstrained profit maximizing water use is `r round(opt_w, digits = 2)` inches, both farmers use up all the allocated quota and use 10 inches of water. Under the proxy quota system, they are allocated the same amount of proxy quota. However, measurement error in proxy quota resulted in effective water quota of 4 and 10 inches for farmer A and B, respectively. Both farmers use their allocated amount of water. Under both proxy and water quota systems, the total water use is 14 inches. Farmer B makes `r pi_dif_2` less under the water quota system compared to the proxy quota system. However, Farmer A makes `r -pi_dif_1` more under the water quota system compared to the proxy quota system. This comes from an important nature of crop production with respect to water: declining marginal impact of water on crop yield. As can be seen in the profit-water relationship, removing an inch of water from 6 inches has much larger negative impact compared to removing an inch of water from 10 inches.

```{r}
#| label: fig-illust-homogeneous
#| fig-cap: "Illustration of profit loss due to the use of proxy for quota-based regulation: a case of homogeneous producers"
#| warning: false
knitr::include_graphics("figures/g_illustration_homogeneous.png")
```

@@

@fig-trading-profit-illustration illustrates the impact of allowing for trading proxy quota using the case of two homogeneous farmers illustrated in @fig-illust-homogeneous. In this illustration, the same water quota of 7 is allocated for both farmers under the water-based systems. No water quota trading would happen as the marginal profit of water is already equated at water use of 7. Under the proxy-base quota system, proxy quota of 7 is allocated for both farmers, but the effective water quota for farmers A and B are 4 and 7, respectively. Once trading of proxy quota is allowed, farmer A would buy `r farmer_A_purchase` proxy quota from farmer B. At these production levels, the marginal profit of quota (not water) are equated across the farmers and no further transfer between them would happen. Trading of proxy quota improves the overall profit to `r profit_after_trade_proxy` $/acre from `r profit_before_trade_quota` $/acre.

@@

While water-quota and proxy-quota trading perform about the same, water-quota always leads to a higher total profit for a given level of realized water use. In other words, to achieve a certain water use goal, water-quota trading is always to more cost-effective than proxy-quota trading. Under water-quota trading, the marginal profit of water is equalized across the farmers, which is a necessary condition to achieve the highest profit for a given level of total water use. Under proxy-quota trading, the marginal profit of proxy is equalized across the farmers, not the marginal profit of water (See Appendix ... for a mathematical proof). However, it is worth emphasizing that the inefficiency caused by the use of proxy is likely to be minimal as shown in @fig-trading-profit. This point is well-illustrated in @fig-trading-profit-illustration, where total profit per acre is `r profit_after_trade_water` and `r profit_after_trade_proxy` under the water-quota and proxy-quota trading system, respsectively.

@fig-trading-profit presents the simulation results of proxy-quota and water-quota trading systems added to @fig-profit-quota-water-het. As you can see at all levels of production heterogeneity levels and the degree of measurement errors, proxy-quota and water-quota trading systems perform almost identical at all levels of realized water use (water-quota trading is always slightly better than proxy-quota trading as explained earlier). Not surprisingly, the benefit of allowing for trading is greater when the degree of measurement errors is larger.

@@

@fig-distributional-equity presents the cumulative probability of the ratio of profit under the proxy-based relative to water-based system for quota (red) and permit trading (blue). Ratio of less than 1 indicates making less profit under the proxy-based system compared to the water-based system. If farmers make just as much profit under proxy-based regulation compared to water-based regulation, then the cumulative probability line would be a vertical line at 1. For example, under the high degree of measurement error and medium heterogeneity scenario, some farmers would make about the half of what they would make under the water quota system. At the lower end of the distribution are farmers who would be constrained severely by water quota, but whose water use estimates are much higher than their actual water use. At the higher end of the distribution are farmers who would be constrained by water quota, but whose water use estimates are much lower than their actual water use. Famres who suffer significantly under the quota system can develop strong dissatisfaction of the quota-based regulation system, which in turn may lead to installing water meter themselves. If they discover the over-estimation of their water use, they may appeal to legal actions against the administrator for their unfair treatment. Allowing quota trading greatly diminishes the distributional inequality, though not completely. This is because unfortunate farmers who suffered from over-estimation of their water use can now at least purchase proxy quota to increase their production level.

### 2024-11-13 Writing/manuscript_typst.tex
minor edits

We now look at simple two-farm examles to build intuition behind the
profit loss due to the use of proxy quota in place of water quota.
Figure~\ref{fig-illust-homegeneous} presents a case with two homegeneous
farmers under water and proxy quota. The red dotted lines indicate the
effective water quota. Under the water quota system, both farmers
receive 7 inches of water quota. Since the unconstrained profit
maximizing water use is 10.94 inches, both farmers use up all the
allocated quota and use 10 inches of water. Under the proxy quota
system, they are allocated the same amount of proxy quota. However,
measurement error in proxy quota resulted in effective water quota of 4
and 10 inches for farmer A and B, respectively. Both farmers use their
allocated amout of water. Under both proxy and water quota systems, the
total water use is 14 inches. Farmer B makes 29.9 less under the water
quota system compared to the proxy quota system. However, Farmer A makes
128.9 more under the water quota system compared to the proxy quota
system. This comes from an important nature of crop production with
respsect to water: declining marginal impact of water on crop yield. As
can be seen in the profit-water relationship, removing an inch of water
from 6 inches has much larger negative impact compared to revmoing an
inch of water from 10 inches.

@@

\caption{\label{fig-illust-homegeneous}Illustration of profit loss due
to the use of proxy for quota-based regulation: a case of homegeneous
producers}

@@

Figure~\ref{fig-trading-profit-illustration} illustrates the impact of
allowing for trading proxy quota using the case of two homogeneous
farmers illustrated in Figure~\ref{fig-illust-homegeneous}. In this
illustration, the same water quota of 7 is allocated for both farmers
under the water-based systems. No water quota trading would happen as
the marginal profit of water is already equated at water use of 7. Under
the proxy-base quota system, proxy quota of 7 is allocated for both
farmers, but the effective water quota for farmers A and B are 4 and 7,
respectively. Once trading of proxy quota is alllowed, farmer A would
buy 1.85 proxy quota from farmer B. At these production levels, the
marginal profit of quota (not water) are equated acros the farmers and
no further transfer between them would happen. Trading of proxy quota
improves the overall profit to 920.08 \$/acre from 831.94 \$/acre.

@@

While water-quota and proxy-quota trading perform about the same,
water-quota always leads to a higher total profit for a given level of
realized water use. In other words, to achieve a certain water use goal,
water-quota trading is always to more cost-effective than proxy-quota
trading. Under water-quota trading, the margial profit of water is
equalized across the farmers, which is a necessary condition to achieve
the highest profit for a given level of total water use. Under
proxy-quota trading, the marginal profit of proxy is equalized across
the farmers, not the margial profit of water (See Appendix \ldots{} for
a mathematical proof). However, it is worth emphasizing that the
inefficiency caused by the use of proxy is likely to be minimal as shown
in Figure~\ref{fig-trading-profit}. This point is well-illustrated in
Figure~\ref{fig-trading-profit-illustration}, where total profit per
acre is 930.91 and 920.08 under the water-quota and proxy-quota trading
system, respsectively.

Figure~\ref{fig-trading-profit} presents the simualtion results of
proxy-quota and water-quota trading systems added to
Figure~\ref{fig-profit-quota-water-het}. As you can see at all levels of
production heterogeneity levels and the degres of measurement errors,
proxy-quota and water-quota trading systems perform almost identical at
all levels of realized water use (water-quota trading is always slightly
better than proxy-quota trading as explained earlier). Not surprisingly,
the benefit of allowing for trading is greater when the degree of
measurement errors is larger.

@@

Figure~\ref{fig-distributional-equity} presents the cumulative
probability of the ratio of profit under the proxy-based relative to
water-based system for quota (red) and permit trading (blue). Ratio of
less than 1 indicates making less profit under the proxy-based system
compared to the water-based system. If farmers make just as much profit
under proxy-based regulation compared to water-based regulation, then
the cumulative probability line would be a vertical line at 1. For
example, under the high degree of measurement error and medium
heterogenenity scenario, some farmers would make about the half of what
they would make under the water quota system. At the lower end of the
distribution are farmers who would be constrained severely by water
quota, but whose water use estiamtes are much higher than their actual
water use. At the higher end of the distribution are farmers who would
be constrained by water quota, but whose water use estiamtes are much
lower than their actual water use. Famres who suffer significantly under
the quota system can develop strong dissatisfaction of the quota-based
regulation system, which in turn may lead to installing water meter
themselves. If they discover the over-estimation of their water use,
they may appeal to legal actions against the administrator for their
unfair treatment. Allowind quota trading greatly diminishes the
distributional inequality, though not completely. This is because
unfortunate farmers who suffered from over-estimation of their water use
can now at least purchase proxy quota to increase their production
level.

>>>>

We now look at simple two-farm examples to build intuition behind the
profit loss due to the use of proxy quota in place of water quota.
Figure~\ref{fig-illust-homogeneous} presents a case with two homogeneous
farmers under water and proxy quota. The red dotted lines indicate the
effective water quota. Under the water quota system, both farmers
receive 7 inches of water quota. Since the unconstrained profit
maximizing water use is 10.94 inches, both farmers use up all the
allocated quota and use 10 inches of water. Under the proxy quota
system, they are allocated the same amount of proxy quota. However,
measurement error in proxy quota resulted in effective water quota of 4
and 10 inches for farmer A and B, respectively. Both farmers use their
allocated amount of water. Under both proxy and water quota systems, the
total water use is 14 inches. Farmer B makes 29.9 less under the water
quota system compared to the proxy quota system. However, Farmer A makes
128.9 more under the water quota system compared to the proxy quota
system. This comes from an important nature of crop production with
respect to water: declining marginal impact of water on crop yield. As
can be seen in the profit-water relationship, removing an inch of water
from 6 inches has much larger negative impact compared to removing an
inch of water from 10 inches.

@@

\caption{\label{fig-illust-homogeneous}Illustration of profit loss due
to the use of proxy for quota-based regulation: a case of homogeneous
producers}

@@

Figure~\ref{fig-trading-profit-illustration} illustrates the impact of
allowing for trading proxy quota using the case of two homogeneous
farmers illustrated in Figure~\ref{fig-illust-homogeneous}. In this
illustration, the same water quota of 7 is allocated for both farmers
under the water-based systems. No water quota trading would happen as
the marginal profit of water is already equated at water use of 7. Under
the proxy-base quota system, proxy quota of 7 is allocated for both
farmers, but the effective water quota for farmers A and B are 4 and 7,
respectively. Once trading of proxy quota is allowed, farmer A would buy
1.85 proxy quota from farmer B. At these production levels, the marginal
profit of quota (not water) are equated across the farmers and no
further transfer between them would happen. Trading of proxy quota
improves the overall profit to 920.08 \$/acre from 831.94 \$/acre.

@@

While water-quota and proxy-quota trading perform about the same,
water-quota always leads to a higher total profit for a given level of
realized water use. In other words, to achieve a certain water use goal,
water-quota trading is always to more cost-effective than proxy-quota
trading. Under water-quota trading, the marginal profit of water is
equalized across the farmers, which is a necessary condition to achieve
the highest profit for a given level of total water use. Under
proxy-quota trading, the marginal profit of proxy is equalized across
the farmers, not the marginal profit of water (See Appendix \ldots{} for
a mathematical proof). However, it is worth emphasizing that the
inefficiency caused by the use of proxy is likely to be minimal as shown
in Figure~\ref{fig-trading-profit}. This point is well-illustrated in
Figure~\ref{fig-trading-profit-illustration}, where total profit per
acre is 930.91 and 920.08 under the water-quota and proxy-quota trading
system, respsectively.

Figure~\ref{fig-trading-profit} presents the simulation results of
proxy-quota and water-quota trading systems added to
Figure~\ref{fig-profit-quota-water-het}. As you can see at all levels of
production heterogeneity levels and the degree of measurement errors,
proxy-quota and water-quota trading systems perform almost identical at
all levels of realized water use (water-quota trading is always slightly
better than proxy-quota trading as explained earlier). Not surprisingly,
the benefit of allowing for trading is greater when the degree of
measurement errors is larger.

@@

Figure~\ref{fig-distributional-equity} presents the cumulative
probability of the ratio of profit under the proxy-based relative to
water-based system for quota (red) and permit trading (blue). Ratio of
less than 1 indicates making less profit under the proxy-based system
compared to the water-based system. If farmers make just as much profit
under proxy-based regulation compared to water-based regulation, then
the cumulative probability line would be a vertical line at 1. For
example, under the high degree of measurement error and medium
heterogeneity scenario, some farmers would make about the half of what
they would make under the water quota system. At the lower end of the
distribution are farmers who would be constrained severely by water
quota, but whose water use estimates are much higher than their actual
water use. At the higher end of the distribution are farmers who would
be constrained by water quota, but whose water use estimates are much
lower than their actual water use. Famres who suffer significantly under
the quota system can develop strong dissatisfaction of the quota-based
regulation system, which in turn may lead to installing water meter
themselves. If they discover the over-estimation of their water use,
they may appeal to legal actions against the administrator for their
unfair treatment. Allowing quota trading greatly diminishes the
distributional inequality, though not completely. This is because
unfortunate farmers who suffered from over-estimation of their water use
can now at least purchase proxy quota to increase their production
level.
